---
title: "Effects on Sample Density"
date: "12/1/2021"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center', fig.height = 8)
```

```{r, include = FALSE}
library(eyetrackSim)
library(bdots)

getFits <- function(ss) {
  ss <- copy(ss)
  fnx <- ss$subPars$fn
  if (fnx == "logistic") {
    fn <- bdots::logistic
  } else if (fnx == "doubleGauss") {
    fn <- bdots::doubleGauss2
  } else if (fnx == "linear") {
    fn <- bdots::linear
  }

  dat <- copy(ss$trialData)
  dat[, group := "grp"]

  if (fnx == "doubleGauss") {
    test <- split(dat, by = "id")
    badid <- vector("numeric", length = 1L)
    for (i in seq_along(test)) {
      rr <-  bdots:::dgaussPars(test[[i]], "looks", "times", TRUE)
      if (length(rr) != 6) badid <- c(badid, i)
    }
    if (length(badid) > 1) {
      bad <- TRUE
      badid <- badid[2:length(badid)]
      dat <- dat[!(id %in% badid), ]
    }
  }
  
  if (fnx == "logistic") {
     fits <- bdotsFit(data = dat,
                   y = "looks",
                   time = "times",
                   subject = "id",
                   group = "group",
                   curveType = logistic(),
                   cores = detectCores() - 1L)
  } else if (fnx == "linear") {
     fits <- bdotsFit(data = dat,
                   y = "looks",
                   time = "times",
                   subject = "id",
                   group = "group",
                   curveType = linear(),
                   cores = detectCores() - 1L)
  } 


  ## Remove bad fits
  idx <- sapply(split(fits, by = "id"), function(x) {
    if (x$fitCode == 6) return(FALSE)
    obj <- x[["fit"]][[1]]
    fv <- fitted(obj)
    res <- residuals(obj)
    cor(fv, fv+res) > 0.8
  })

  fits <- fits[idx, ]
}

## Coefficient matrix for simulation, based on valid fits
# returns matrix
getSimCoef <- function(ss, fits) {
  ss <- copy(ss)
  sim_coef <- ss$subPars$pars
  sim_coef <- sim_coef[id %in% fits$id, ]
  sim_coef[, id := NULL]
  sim_coef <- as.matrix(sim_coef)
}

plotY <- function(idx, mm = NULL) {
  oldpar <- par(mfrow = c(2,1))
  on.exit(par(oldpar))
  plot(times, fity[, idx], type = 'l', ylim = c(0, 1), lwd = 2,
       main = paste0("Subject ", idx, "\n", mm))
  lines(times, simy[, idx], type = 'l', col = 'steelblue', lwd = 2)
  legend(x = 1300, y = 0.4, legend = c("Underlying", "bdots"),
         col = c("steelblue", "black"), lty = 1, lwd = 2)
  fix <- sim_l$fixations[id == idx & starttime != 0, ]
  plot(density(fix$starttime), main = "saccade density")
}
```

# Overview

Here, we ran simulations with a linear and nonlinear underlying curve, including conditions for FBST = TRUE/FALSE.

We then repeat simulations with nonlinear, removing the random saccade component and replacing it with saccades every 10ms and 50ms. We left the initial onset time and initial fixation to be random to prevent staggering. That way, for each subject's trial, the actual points sampled will differ, increasing sample space

# Linear Simulation 

## FBST = FALSE {.tabset}

```{r}
sim_l <- runSim(nsub = 2L, fnct = "linear", fbst = FALSE)

fits <- getFits(sim_l)

sim_coef <- getSimCoef(sim_l, fits)
fit_coef <- coef(fits)

## Consider now the *actual* curves
fity <- sapply(split(fits, by = "id"), function(x) {
  fitted(x[['fit']][[1]])
})
simy <- apply(sim_coef, 1, linear_f, t = times)

mm <- "linear, FBST = FALSE"
# for (i in 1:2) {
#   plotY(i, mm)
# }
```

### Sub 1

```{r}
plotY(1, mm)
```

### Sub 2

```{r}
plotY(2, mm)
```

## FBST = TRUE {.tabset}

```{r}
sim_l <- runSim(nsub = 2L, fnct = "linear", fbst = TRUE)

fits <- getFits(sim_l)

sim_coef <- getSimCoef(sim_l, fits)
fit_coef <- coef(fits)

## Consider now the *actual* curves
fity <- sapply(split(fits, by = "id"), function(x) {
  fitted(x[['fit']][[1]])
})
simy <- apply(sim_coef, 1, linear_f, t = times)

mm <- "linear, FBST = TRUE"
# for (i in 1:2) {
#   plotY(i, mm)
# }
```

### Sub 1

```{r}
plotY(1, mm)
```

### Sub 2

```{r}
plotY(2, mm)
```

# Logistic Simulation 

## FBST=FALSE {.tabset}

```{r}
sim_l <- runSim(nsub = 4L, fnct = "logistic", fbst = FALSE)

fits <- getFits(sim_l)

sim_coef <- getSimCoef(sim_l, fits)
fit_coef <- coef(fits)

## Consider now the *actual* curves
fity <- sapply(split(fits, by = "id"), function(x) {
  fitted(x[['fit']][[1]])
})
simy <- apply(sim_coef, 1, logistic_f, t = times)

mm <- "logistic, FBST = FALSE"
# for (i in 1:4) {
#   plotY(i, mm)
# }
```

### Sub 1

```{r}
plotY(1, mm)
```

### Sub 2

```{r}
plotY(2, mm)
```

### Sub 3

```{r}
plotY(3, mm)
```

### Sub 4

```{r}
plotY(4, mm)
```

## FBST=TRUE {.tabset}

```{r}
sim_l <- runSim(nsub = 4L, fnct = "logistic", fbst = TRUE)

fits <- getFits(sim_l)

sim_coef <- getSimCoef(sim_l, fits)
fit_coef <- coef(fits)

## Consider now the *actual* curves
fity <- sapply(split(fits, by = "id"), function(x) {
  fitted(x[['fit']][[1]])
})
simy <- apply(sim_coef, 1, logistic_f, t = times)

mm <- "logistic, FBST = TRUE"
# for (i in 1:4) {
#   plotY(i, mm)
# }
```

### Sub 1

```{r}
plotY(1, mm)
```

### Sub 2

```{r}
plotY(2, mm)
```

### Sub 3

```{r}
plotY(3, mm)
```

### Sub 4

```{r}
plotY(4, mm)
```


# Density Sampling (logistic) 

## d = 50 {.tabset}

```{r}
sim_l <- runSim_fixed(nsub = 2L, fnct = "logistic", sampDensity = 50L)

fits <- getFits(sim_l)

sim_coef <- getSimCoef(sim_l, fits)
fit_coef <- coef(fits)

## Consider now the *actual* curves
fity <- sapply(split(fits, by = "id"), function(x) {
  fitted(x[['fit']][[1]])
})
simy <- apply(sim_coef, 1, logistic_f, t = times)

mm <- "logistic, sampDensity = 50"
# for (i in 1:2) {
#   plotY(i, mm)
# }
```

### Sub 1

```{r}
plotY(1, mm)
```

### Sub 2

```{r}
plotY(2, mm)
```

## d = 10 {.tabset}

```{r}
sim_l <- runSim_fixed(nsub = 2L, fnct = "logistic", sampDensity = 10L)

fits <- getFits(sim_l)

sim_coef <- getSimCoef(sim_l, fits)
fit_coef <- coef(fits)

## Consider now the *actual* curves
fity <- sapply(split(fits, by = "id"), function(x) {
  fitted(x[['fit']][[1]])
})
simy <- apply(sim_coef, 1, logistic_f, t = times)

mm <- "logistic, sampDensity = 10"
# for (i in 1:2) {
#   plotY(i, mm)
# }
```

### Sub 1

```{r}
plotY(1, mm)
```

### Sub 2

```{r}
plotY(2, mm)
```
